An agent-based model for modal shift in public transport

### 2021-01-31 abstract.tex
submission

\begin{abstract}
Modal shift in public transport as a consequence of a disruption on a line has in some cases unforeseen consequences such as an increase in congestion in the rest of the network. How information is provided to users and their behavior plays a central role in such configurations. We introduce here a simple and stylised agent-based model aimed at understanding the impact of behavioral parameters on modal shift. The model is applied on a case study based on a stated preference survey for a segment of Paris suburban train network. We systematically explore the parameter space and show non-trivial patterns of congestion for some values of discrete choice parameters linked to perceived wait time and congestion. Work in progress include the application of optimization algorithms to the model to search for optimal compromises between congestion in different modes.
\end{abstract}

@@

%%%%%%%%%%%%
\begin{figure}[t]\vspace*{4pt}
\centerline{\includegraphics[width=0.45\linewidth]{figures/Fig1.png}}
\caption{Results of the declared preference survey. \textit{(Left)} Number of times a month users experience a disruption; \textit{(Middle)} Behavior of users when no information is given; \textit{(Right)} Behavior of users when a 10 minutes traffic stop is announced.\label{fig:fig1}}
\end{figure}
%%%%%%%%%%%%

>>>>

\begin{abstract}
Modal shift in public transport as a consequence of a disruption on a line has in some cases unforeseen consequences such as an increase in congestion in the rest of the network. How information is provided to users and their behavior plays a central role in such configurations. We introduce here a simple and stylised agent-based model aimed at understanding the impact of behavioral parameters on modal shift. The model is applied on a case study based on a stated preference survey for a segment of Paris suburban train network. We systematically explore the parameter space and show non-trivial patterns of congestion for some values of discrete choice parameters linked to perceived wait time and congestion. Work in progress includes the application of optimization algorithms to the model to search for optimal compromises between congestion in different modes.
\end{abstract}

@@

%%%%%%%%%%%%
\begin{figure}[t]\vspace*{4pt}
\centerline{\includegraphics[width=0.45\linewidth]{figures/Fig1.png}}
\caption{Results of the stated preference survey. \textit{(Left)} Number of times a month users experience a disruption; \textit{(Middle)} Behavior of users when no information is given; \textit{(Right)} Behavior of users when a 10 minutes traffic stop is announced.\label{fig:fig1}}
\end{figure}
%%%%%%%%%%%%
